{ \sffamily \LARGE Electronic supplementary material}\\{\bf \sffamily \LARGE Evolution of reciprocity with limited payoff memory

### 2023-10-29 paper/main.tex
make "dynamics" plural

In each case, the evolutionary dynamics follows a similar cyclic pattern~\citep[as previously described in Refs.][]{imhof2010stochastic, Nowak1992tit}:
Resident populations of defectors are most likely invaded by strategies close to \tft. 
Once the population adopts conditionally cooperative strategies  $(1,1,q)$, neutral drift may introduce larger values of generosity $q$. 
If the resident's generosity~$q$ violates the conditions~\eqref{Eq:PerfectMemory} and~\eqref{Eq:LimitedMemory}, defectors can re-invade, and the cycle starts again. 
The overall cooperation rate, averaged over many time steps, depends on how much time the process spends near \alld{} on the one hand, and near the strip of conditionally cooperative strategies on the other. 
For perfect payoff memory, the overall cooperation rate is substantial. 
It is 52\% for low benefits, and 98\% for high benefits. 
For limited payoff memory, the evolving cooperation rates are smaller but strictly positive, with 37\% cooperation for low benefits and 51\% cooperation for high benefits (\FigBaseResults).

@@

Our main contribution is an application of these ideas to direct reciprocity, which is one of the key mechanisms to explain why unrelated individuals might cooperate~\citep{nowak:Science:2006}. 
According to this mechanism, cooperation pays if it makes the interaction partner more cooperative in future. 
To describe which strategies of direct reciprocity are most effective, the previous theoretical literature assumes that the evolutionary dynamics is determined by the players' expected payoffs~\citep{brauchli:JTB:1999,brandt:JTB:2006,ohtsuki:JTB:2007b,szolnoki:pre:2009b,imhof2010stochastic,van-segbroeck:prl:2012,grujic:jtb:2012,Martinez2012,stewart:pnas:2013,pinheiro:PLoSCB:2014,stewart:games:2015,Baek2016,McAvoy:ProcA:2019,glynatsi:SCR:2020,Schmid:PlosCB:2022,Murase:SciRep:2022}.
To the extent that strategies are learned (not inherited), this assumption seems to impose rather stringent requirements on the individuals' cognitive abilities. 
In the most extreme case, this would require individuals to remember (or compute) their payoffs against all population members, for all possible ways in which their repeated games may unfold. 
This assumption introduces a curious inconsistency in how these models represent an individual's cognitive abilities. 
For playing their games, individuals are often assumed to only recall the outcome of the very last round. 
Yet to update their strategies, individuals are implicitly assumed to have a record of the outcome of all rounds, across all interaction partners.

>>>>

In each case, the evolutionary dynamics follow a similar cyclic pattern~\citep[as previously described in Refs.][]{imhof2010stochastic, Nowak1992tit}:
Resident populations of defectors are most likely invaded by strategies close to \tft. 
Once the population adopts conditionally cooperative strategies  $(1,1,q)$, neutral drift may introduce larger values of generosity $q$. 
If the resident's generosity~$q$ violates the conditions~\eqref{Eq:PerfectMemory} and~\eqref{Eq:LimitedMemory}, defectors can re-invade, and the cycle starts again. 
The overall cooperation rate, averaged over many time steps, depends on how much time the process spends near \alld{} on the one hand, and near the strip of conditionally cooperative strategies on the other. 
For perfect payoff memory, the overall cooperation rate is substantial. 
It is 52\% for low benefits, and 98\% for high benefits. 
For limited payoff memory, the evolving cooperation rates are smaller but strictly positive, with 37\% cooperation for low benefits and 51\% cooperation for high benefits (\FigBaseResults).

@@

Our main contribution is an application of these ideas to direct reciprocity, which is one of the key mechanisms to explain why unrelated individuals might cooperate~\citep{nowak:Science:2006}. 
According to this mechanism, cooperation pays if it makes the interaction partner more cooperative in future. 
To describe which strategies of direct reciprocity are most effective, the previous theoretical literature assumes that the evolutionary dynamics are determined by the players' expected payoffs~\citep{brauchli:JTB:1999,brandt:JTB:2006,ohtsuki:JTB:2007b,szolnoki:pre:2009b,imhof2010stochastic,van-segbroeck:prl:2012,grujic:jtb:2012,Martinez2012,stewart:pnas:2013,pinheiro:PLoSCB:2014,stewart:games:2015,Baek2016,McAvoy:ProcA:2019,glynatsi:SCR:2020,Schmid:PlosCB:2022,Murase:SciRep:2022}.
To the extent that strategies are learned (not inherited), this assumption seems to impose rather stringent requirements on the individuals' cognitive abilities. 
In the most extreme case, this would require individuals to remember (or compute) their payoffs against all population members, for all possible ways in which their repeated games may unfold. 
This assumption introduces a curious inconsistency in how these models represent an individual's cognitive abilities. 
For playing their games, individuals are often assumed to only recall the outcome of the very last round. 
Yet to update their strategies, individuals are implicitly assumed to have a record of the outcome of all rounds, across all interaction partners.
